Notes on Perturbational Quantities

### 2011-06-16 docs/pert_notes/pert.tex
more work on the different enthalpy types...

%-----------------------------------------------------------------------------
% density
%-----------------------------------------------------------------------------
\section{Density Evolution}
The full density evolution equation is
\begin{eqnarray}
\frac{\partial\rho}{\partial t} &=& -\nabla\cdot(\rho\Ub) \nonumber \\
&=& -\Ub\cdot\nabla\rho - \rho\nabla\cdot\Ub \, . \label{rho equation}
\end{eqnarray}
The species are evolved according to
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& -\nabla\cdot(\rho\Ub X_k) + \rho \omegadot_k \nonumber \\
&=& -\Ub\cdot\nabla(\rho X_k) - \rho X_k \nabla\cdot\Ub + \rho \omegadot_k \, . \label{species equation}
\end{eqnarray}
In practice, only the species evolution equation is evolved, and the
total density is set as
\begin{equation}
\rho = \sum_k (\rho X_k)
\end{equation}
To advance $(\rho X_k)$ to the next timestep, we need to predict a
time-centered, interface state.  Algebraically, there are multiple
paths to get this interface state---we can predict $(\rho X)$ to the
edges as a single quantity, or predict $\rho$ and $X$ separately
(either in full or perturbation form).  In the notes below, we use the
subscript `{\tt edge}' to indicate what quantity was predicted to the
edges.  In MAESTRO, the different methods of computing $(\rho X)$ on
edges are controlled by the {\tt species\_pred\_type} parameter.  The
resulting edge state is shown in the following table:

@@

\noindent {\tt species\_pred\_type = predict\_rhoprime\_and\_X}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = -\nabla\cdot(\rho X_k\Ub) = 
-\nabla\cdot\left\{\left[\left({\rho_0}^{n+\myhalf,{\rm avg}}
+ \rho'_\mathrm{edge} \right)(X_k)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation} \\

\noindent {\tt species\_pred\_type = predict\_rhoX}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = -\nabla\cdot(\rho X_k\Ub) = 
-\nabla\cdot\left\{\left[\left(\rho X_k \right)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation}

\noindent {\tt species\_pred\_type = predict\_rho\_and\_X}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = -\nabla\cdot(\rho X_k\Ub) = 
-\nabla\cdot\left\{\left[\rho_\mathrm{edge} (X_k)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation}

@@

Note: only the default {\tt enthalpy\_pred\_type = 1} is guaranteed to work
with {\tt species\_pred\_type > 1}. \\

Maestro solves an enthalpy equation.  
The full enthalpy equation is
\begin{eqnarray}
\frac{\partial(\rho h)}{\partial t} &=& -\nabla\cdot(\rho h \Ub) + \frac{Dp_0}{Dt} 
+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\
&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.
\end{eqnarray}
%The full temperature equation is
%\begin{equation}
%\frac{\partial T}{\partial t} = -\Ub\cdot\nabla T
%+ \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi
%+ (\Ubt \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 
%+ \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.
%\end{equation}
Due to Strang-splitting of the reactions,the call to {\tt
  react\_state} has already been made.  Hence, the goal is to compute
an edge state enthalpy starting from $(\rho h)^{(1)}$ using an
enthalpy equation that does not include the $\rho H_{\rm nuc}$ and
$\rho H_{\rm ext}$ terms, where were already accounted for in {\tt
  react\_state}, so our equation becomes
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{``(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}
Subtracting (\ref{rhoh0 equation}) from (\ref{rhoh equation}) and
rearranging terms gives the perturbational enthalpy equation
\begin{eqnarray}
\frac{\partial(\rho h)'}{\partial t} &=& -\nabla\cdot[(\rho h)'\Ub] 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} 
+ \nabla\cdot\kth\nabla T\nonumber \\
&=& -\Ub\cdot\nabla(\rho h)' \underbrace{- (\rho h)'\nabla\cdot\Ub 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r}
+ \nabla\cdot\kth\nabla T}_{``(\rho h)' ~ \text{force}"}, \label{rhohprime equation}
\end{eqnarray}

@@

@@

To update the enthalpy, we need to compute an interface state for
$(\rho h)$.  As with the species evolution, there are multiple
quantities we can predict to the interfaces to form this state,
controlled by {\tt enthalpy\_pred\_type}.  A complexity of the
enthalpy evolution is that the formation of this edge state will
depend on {\tt species\_pred\_type}.  Table~\ref{table:pred:hoverview}
gives a summary
of the {\tt enthalpy\_pred\_type} behavior.

@@

\begin{table*}[h]
\centering
\caption{Forcing term into {\tt make\_edge\_scal} \newline}
\label{table:pred:hforce}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c}
\hline
\hline
{\tt enthalpy\_pred\_type} &   {advective force} \\
\hline
1 / {\tt predict\_rhohprime} $((\rho h)^\prime)$ &  $(\Ubt \cdot \er) \frac{\partial p_0}{\partial r} - 
 (\rho h)^\prime \; \nabla \cdot (\Ubt+w_0 \er) - 
 \nabla \cdot (\Ubt (\rho h)_0) + \nabla \cdot \kth \nabla T$ \\
2 / {\tt predict\_h}  $(h)$ & $\frac{1}{\rho} \left [\psi + (\Ubt \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\
3 / {\tt predict\_T\_then\_rhohprime} $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} \right ] + \nabla \cdot \kth \nabla T \right \}$ \\
4 / {\tt predict\_T\_then\_h}  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\Ubt \cdot \er)
\frac{\partial p_0}{\partial r}\right ] +  \nabla \cdot \kth \nabla T \right\}$ \\
\hline
\end{tabular}
\end{table*}

@@

\subsection{Predicting $(\rho h)'$ at edges}\label{Predicting rhohprime at edges}

where the first two terms in $(\rho h)'$ force are computed in 
{\tt modify\_scal\_force}, and the last two terms are accounted for in
{\tt mkrhohforce}.  For spherical problems, we have found that a different 
representation of the pressure term in the $(\rho h)'$ force gives better
results, namely:
\begin{equation}
(\Ubt \cdot \er)\frac{\partial p_0}{\partial r} \equiv \Ubt\cdot\nabla p_0 = 
\nabla\cdot(\Ubt p_0) - p_0\nabla\cdot\Ubt.
\end{equation}

We define $(\rho h)' = (\rho h)^{(1)} - (\rho h)_0^n$.  Then we predict 
$(\rho h)'$ to edges using {\tt make\_edge\_scal} in {\tt enthalpy\_advance} 
and the underbraced term in (\ref{rhohprime equation}) as the forcing.

\subsection{Predicting $(\rho h)_0$ at edges}
We use an analogous procedure described in Section \ref{Predicting
rho0 at edges} for computing $\rho_0^{n+\myhalf,\rm{avg}}$ to obtain 
$(\rho h)_0^{n+\myhalf,\rm{avg}}$, i.e., 
$(\rho h)_0^{n+\myhalf,{\rm avg}} = [(\rho h)_0^{n} + (\rho h)_0^{n+1}]/2$.

\subsection{Computing $\rho h$ at edges}
We use an analogous procedure described in Section \ref{Computing rho
  at edges} for computing $\rho$ at edges to compute $\rho h$ at
edges.  For spherical, however, instead of computing $(\rho h)_0$ to
edges directly, we compute $\rho$ and $h$ separately, and multiply to
get $(\rho h)_0$.

\subsection{Advancing $\rho h$}
We update the enthalpy analogously to the species update in 
Section \ref{Advancing rhoX_k}.  The forcing term does not include reaction
source terms accounted for in {\bf React State}.
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\nabla\cdot(\rho h\Ub) = 
-\nabla\cdot\left\{\left[(\rho h)_0^{n+\myhalf,{\rm avg}} 
+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .
\end{equation}

\begin{table*}
\begin{center}
\caption{When predicting temp ... (conversion done by {\tt makeRhoHfromT}) \newline}
\begin{tabular}{c|c|c|c}
\hline
\hline
{type} & {Inputs } & {EOS inputs} & {output} \\
\hline
3 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ &  $(\rho h)^\prime = \rho h - (\rho h)_0$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
 4 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ & $h$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

%-----------------------------------------------------------------------------
% density
%-----------------------------------------------------------------------------
\section{Density Evolution}

\subsection{Basic equations}

The full density evolution equation is
\begin{eqnarray}
\frac{\partial\rho}{\partial t} &=& -\nabla\cdot(\rho\Ub) \nonumber \\
&=& -\Ub\cdot\nabla\rho - \rho\nabla\cdot\Ub \, . \label{rho equation}
\end{eqnarray}
The species are evolved according to
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& -\nabla\cdot(\rho\Ub X_k) + \rho \omegadot_k \nonumber \\
&=& -\Ub\cdot\nabla(\rho X_k) - \rho X_k \nabla\cdot\Ub + \rho \omegadot_k \, . \label{species equation}
\end{eqnarray}
In practice, only the species evolution equation is evolved, and the
total density is set as
\begin{equation}
\rho = \sum_k (\rho X_k)
\end{equation}
To advance $(\rho X_k)$ to the next timestep, we need to predict a
time-centered, interface state.  Algebraically, there are multiple
paths to get this interface state---we can predict $(\rho X)$ to the
edges as a single quantity, or predict $\rho$ and $X$ separately
(either in full or perturbation form).  In the notes below, we use the
subscript `{\tt edge}' to indicate what quantity was predicted to the
edges.  In MAESTRO, the different methods of computing $(\rho X)$ on
edges are controlled by the {\tt species\_pred\_type} parameter.  The
resulting edge state is shown in the following table:

@@

\noindent {\tt species\_pred\_type = predict\_rhoprime\_and\_X}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = 
-\nabla\cdot\left\{\left[\left({\rho_0}^{n+\myhalf,{\rm avg}}
+ \rho'_\mathrm{edge} \right)(X_k)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation} \\

\noindent {\tt species\_pred\_type = predict\_rhoX}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = 
-\nabla\cdot\left\{\left[\left(\rho X_k \right)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation}

\noindent {\tt species\_pred\_type = predict\_rho\_and\_X}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = 
-\nabla\cdot\left\{\left[\rho_\mathrm{edge} (X_k)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation}

@@

\subsection{Basic equations}

Maestro solves an enthalpy equation.  
The full enthalpy equation is
\begin{eqnarray}
\frac{\partial(\rho h)}{\partial t} &=& -\nabla\cdot(\rho h \Ub) + \frac{Dp_0}{Dt} 
+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\
&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.
\end{eqnarray}
%The full temperature equation is
%\begin{equation}
%\frac{\partial T}{\partial t} = -\Ub\cdot\nabla T
%+ \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi
%+ (\Ubt \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 
%+ \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.
%\end{equation}
Due to Strang-splitting of the reactions,the call to {\tt
  react\_state} has already been made.  Hence, the goal is to compute
an edge state enthalpy starting from $(\rho h)^{(1)}$ using an
enthalpy equation that does not include the $\rho H_{\rm nuc}$ and
$\rho H_{\rm ext}$ terms, where were already accounted for in {\tt
  react\_state}, so our equation becomes
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{``(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}

\subsubsection{Perturbational enthalpy formulation}

Subtracting (\ref{rhoh0 equation}) from (\ref{rhoh equation}) and
rearranging terms gives the perturbational enthalpy equation
\begin{eqnarray}
\frac{\partial(\rho h)'}{\partial t} &=& -\nabla\cdot[(\rho h)'\Ub] 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} 
+ \nabla\cdot\kth\nabla T\nonumber \\
&=& -\Ub\cdot\nabla(\rho h)' \underbrace{- (\rho h)'\nabla\cdot\Ub 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r}
+ \nabla\cdot\kth\nabla T}_{``(\rho h)' ~ \text{force}"}, \label{rhohprime equation}
\end{eqnarray}

\subsubsection{Temperature formulation}

@@

\subsubsection{Pure enthalpy formulation}

@@

\subsubsection{Prediction requirements}

To update the enthalpy, we need to compute an interface state for
$(\rho h)$.  As with the species evolution, there are multiple
quantities we can predict to the interfaces to form this state,
controlled by {\tt enthalpy\_pred\_type}.  A complexity of the
enthalpy evolution is that the formation of this edge state will
depend on {\tt species\_pred\_type}.

@@

\noindent Note: the various {\tt enthalpy\_pred\_type}s are only
guaranteed to work with {\tt species\_pred\_type = 1}.

Table~\ref{table:pred:hoverview}
gives a summary
of the {\tt enthalpy\_pred\_type} behavior.

\begin{table*}[h]
\centering
\caption{Forcing term into {\tt make\_edge\_scal} \newline}
\label{table:pred:hforce}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c}
\hline
\hline
{\tt enthalpy\_pred\_type} &   {advective force} \\
\hline
1 / {\tt predict\_rhohprime} $((\rho h)^\prime)$ &  
 $-(\rho h)^\prime \; \nabla \cdot (\Ubt+w_0 \er) - 
 \nabla \cdot (\Ubt (\rho h)_0) + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T$ \\
2 / {\tt predict\_h}  $(h)$ & $\frac{1}{\rho} \left [\psi + (\Ubt \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\
3 / {\tt predict\_T\_then\_rhohprime} $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} \right ] + \nabla \cdot \kth \nabla T \right \}$ \\
4 / {\tt predict\_T\_then\_h}  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\Ubt \cdot \er)
\frac{\partial p_0}{\partial r}\right ] +  \nabla \cdot \kth \nabla T \right\}$ \\
\hline
\end{tabular}
\end{table*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_rhohprime}}

Here we wish to construct $\left [ (\rho h)_0 + (\rho
  h)'_\mathrm{edge} \right ]$ by predicting $(\rho h)'$ to the edges.

\subsubsection{Predicting $(\rho h)'$ at edges}\label{Predicting rhohprime at edges}

We define $(\rho h)' = (\rho h)^{(1)} - (\rho h)_0^n$.  Then we predict 
$(\rho h)'$ to edges using {\tt make\_edge\_scal} in {\tt enthalpy\_advance} 
and the underbraced term in (\ref{rhohprime equation}) as the forcing (see
also table~\ref{table:pred:hforce} for the forcing term).
The first two terms in $(\rho h)'$ force are computed in 
{\tt modify\_scal\_force}, and the last two terms are accounted for in
{\tt mkrhohforce}.  For spherical problems, we have found that a different 
representation of the pressure term in the $(\rho h)'$ force gives better
results, namely:
\begin{equation}
(\Ubt \cdot \er)\frac{\partial p_0}{\partial r} \equiv \Ubt\cdot\nabla p_0 = 
\nabla\cdot(\Ubt p_0) - p_0\nabla\cdot\Ubt.
\end{equation}

\subsubsection{Predicting $(\rho h)_0$ at edges}
We use an analogous procedure described in Section \ref{Predicting
rho0 at edges} for computing $\rho_0^{n+\myhalf,\rm{avg}}$ to obtain 
$(\rho h)_0^{n+\myhalf,\rm{avg}}$, i.e., 
$(\rho h)_0^{n+\myhalf,{\rm avg}} = [(\rho h)_0^{n} + (\rho h)_0^{n+1}]/2$.

For spherical, however, instead of computing $(\rho h)_0$ to edges
directly, we compute $\rho_0$ and $h_0$ separately at the edges, and
multiply to get $(\rho h)_0$.

\subsubsection{Computing $\rho h$ at edges}
We use an analogous procedure described in Section \ref{Computing rho
  at edges} for computing $\rho$ at edges to compute $\rho h$ at
edges.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_h}}

Here we wish to construct $\left (\rho_0 + \rho'_\mathrm{edge} \right
) h_\mathrm{edge}$ by predicting $h$ to the edges.

\subsubsection{Predicting $h$ at edges}

We define $h = (rho h)^{(1)}/rho^{(1)}$.  Then we predict $h$ to edges
using {\tt make\_edge\_scal} in {\tt enthalpy\_advance} and the
underbraced term in Eq.~\ref{h equation labeled} as the forcing (see
also table~\ref{table:pred:hforce}).  This force is computed by
{\tt mkrhohforce} and then divided by $\rho$.  Note: {\tt mkrhoforce}
knows about the different {\tt enthalpy\_pred\_type}s and computes
the correct force for this type.

\subsubsection{Computing $\rho h$ at edges}

We use the same procedure described in Section \ref{Computing rho at
  edges} to computing $\rho$ at edges from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_rhohprime}}

Here we wish to construct $\left [ (\rho h)_0 + (\rho
  h)'_\mathrm{edge} \right ]$ by predicting $T$ to the edges and then
converting this to $(\rho h)'_\mathrm{edge}$ via the EOS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_rhohprime}}

Here we wish to construct $\left (\rho_0 + \rho'_\mathrm{edge} \right
) h_\mathrm{edge}$ by predicting $T$ to the edges and then converting
this to $h_\mathrm{edge}$ via the EOS.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Advancing $\rho h$}
We update the enthalpy analogously to the species update in 
Section \ref{Advancing rhoX_k}.  The forcing term does not include reaction
source terms accounted for in {\bf React State}.
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = 
-\nabla\cdot\left\{\left[(\rho h)_0^{n+\myhalf,{\rm avg}} 
+ (\rho h)'\right]\left(\Ubt + w_0\eb_r\right)\right\} + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} + \psi  \enskip .
\end{equation}

\begin{table*}[h]
\begin{center}
\caption{When predicting temp ... (conversion done by {\tt makeRhoHfromT}) \newline}
\begin{tabular}{c|c|c|c}
\hline
\hline
{type} & {Inputs } & {EOS inputs} & {output} \\
\hline
3 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ &  $(\rho h)^\prime = \rho h - (\rho h)_0$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
 4 & $X$ and $\rho^\prime$ & $\rho = \rho_0 + \rho^\prime$ & $h$ \\
   &                   & $   X = $ given & \\
   &                   &                 & \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}[h]
\begin{center}
\caption{Quantity that is created in {\tt mkflux} and passed into {\tt update\_scal}\newline\
}
\begin{tabular}{c|c|c|c|c}
       &            &              &\multicolumn{2}{c}{Forcing Term} \\
{type} & {Species } & {$(\rho h)$} & {$(\rho X)$} & {$(\rho h)$} \\
\hline 
1 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
2 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
3 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0)\left [(\rho h)_0 + (\rho h)^\prime\right]$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}$ \\[2mm]
4 & $(\Ubt+w_0)(\rho_0+\rho^\prime) X          $ & $(\Ubt+w_0) (\rho_0+\rho^\prime) h$ & 0 & $ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} $ \\[2mm]
\hline
\end{tabular}
\end{center}
\end{table*}
